Leadership across cultures and contexts: an exploratory analysis

### 2020-05-02 leadership_across_cultures_contexts.Rmd
Other minor discussion changes.

<!-- ADD CITTATION IN STATUS  -->
<!-- cheng_why_2020 -->

This exploratory study extracted the qualities, functions, benefits, and costs of leadership from the ethnographic record. The variables on leader qualities and functions were *not* determined prior to the study but were instead identified and coded during multiple passes through `r nrow(text_records)` texts on leadership obtained from the eHRAF (see Methods section). Our results therefore represent the broadest and most comprehensive view of the qualities of leaders (i.e., the types of people that occupy leadership roles), the functions of leaders (i.e., what leaders do), and the costs and benefits of leadership for both leaders and followers across a diverse and culturally representative sample of the ethnographic record. These results reveal universal dimensions of human leadership while also suggesting important variation by group type, subsistence type, and sex of the leader.

## Effects of culture and context on human leadership

The distribution of text records by group and subsistence type suggests leaders emerge within similar social domains among populations with varied subsistence strategies, but at variable frequencies. See Figure \@ref(fig:grouptype). Exploratory analyses identified both universal and variable dimensions of human leadership, across cultures and contexts.

@@

In groups of all subsistence types (e.g., hunter-gatherers, pastoralists) leaders emerge across a similar range of group types, including at lower-level social units such as within residential groups and kin groups; within specialized groups such as religious, economic, or military groups; and in political contexts at the community and supracommunity levels. A large percentage of text records in all subsistence groups document political leadership at the community level. Leadership at the supracommunity level is also common across all subsistence groups save hunter-gatherers, which are largely autonomous. Economic, military, and religious group leadership, although relatively less frequent, are fairly consistently represented across subsistence levels.

@@

```{r glmmcoefs}
# kable(all_coefs)

>>>>

This exploratory study extracted quantitative measures of the qualities, functions, benefits, and costs of leadership from the ethnographic record. The variables on leader qualities and functions were *not* determined prior to the study but were instead identified and coded during multiple passes through `r nrow(text_records)` texts on leadership obtained from the eHRAF (see Methods section). These data therefore represent the broadest and most comprehensive view of the qualities of leaders (i.e., the types of people that occupy leadership roles), the functions of leaders (i.e., what leaders do), and the costs and benefits of leadership for both leaders and followers across a diverse and culturally representative sample of the ethnographic record. Results revealed universal dimensions of human leadership as well as important variation by group context, subsistence type, and sex of the leader.

## Culture, context, and human leadership

The distribution of text records by group and subsistence type suggests leaders emerge within similar social contexts among populations with varied subsistence strategies, but at variable frequencies. See Figure \@ref(fig:grouptype). Exploratory analyses identified both universal and variable dimensions of human leadership across cultures and contexts.

@@

In groups of all subsistence types (e.g., hunter-gatherers, pastoralists) leaders emerge across a similar range of group types, including at lower-level social units such as within residential groups and kin groups; within specialized groups such as religious, economic, and military groups; and in political contexts at the community and supracommunity levels. A large percentage of text records in all subsistence groups documented political leadership at the community level. Leadership at the supracommunity level was also common across all subsistence groups save hunter-gatherers, which are largely autonomous. Economic, military, and religious group leadership, although relatively less frequent, were fairly consistently represented across subsistence levels.

@@

```{r glmmcoefs }
# kable(all_coefs)
